\section{Future Work}

Having considered the success of this project in comparison to its objectives, I'd like to suggest some key areas where the project needs work to achieve further success.

\subsection{Further investigation of proxy re-encryption}

Proxy re-encryption has been used in this project to answer the question of whether truly decentralised privacy and data sharing can exist. In this way proxy re-encryption acts as a facilitator to the project. However, the current implementation faces security issues as evaluated above. Further investigation of the suitability of proxy re-encryption for the project's objectives, and whether any other schemes might be more suitable, is necessary to determine whether the evaluated security issues can be overcome by modification, extension, or replacement of the scheme.

\subsection{ElGamal in the browser}

One of the greatest implementation issues is the dependency on having a Java runtime available to act as a local encryption proxy. Due to time constraints, this iteration of the project was not able to convert the Java-written cryptography library which implements the AFGH scheme into a JavaScript and Web compatible layer. Whilst the time and effort to implement this improvement would be very great, the value of making a secure JavaScript layer could enable cross-platform, cross-device use of the system and allow widespread availability.

\subsection{Formal monetisation}

Hypothetically a service which is designed to support the public interest shouldn't be a profitable entity, but one that re-invests in itself. However, if this project were commissioned as a decentralised service to support a public sector institution (such as the NHS), the participants in the network (those processing and validating transactions) would require some form of payment. I suggested in the evaluation that the transaction costs imposed by Ethereum, whilst irrelevant for the project's proof of concept, function as a means of regulating the service and incentivising honest (and timely) transaction processing.

I propose that investigation into the monetisation of the platform, particularly with a view to public sector use, would be of great benefit.

\subsection{Storage Blockchain}

Finally, we question whether any current blockchain is in fact suitable for this application, and furthermore whether a single blockchain could run this application or whether alternative proposals might be more suitable.
