\subsection{Objectives}

This project aims to re-imagine how we share data from the point of view of prioritising privacy, control, and availability. It is my belief that through decentralisation it is possible to have a system which no one entity controls or owns, but which every willing and able entity can participate in, privately.

As a foreword to discovering possible implementation and design choices, it is important to set out the objectives of the project and keep these in context. The primary objective of this project is to \textbf{discover whether a fully decentralised, private data sharing platform can exist}. The meaning of private in this context refers to hiding the content of the underlying data. The following secondary objectives follow from the primary objective:

\begin{itemize}
  \item \textbf{End-to-end Encryption} \\
  Must only share data which is encrypted and decrypted client-side. No unencrypted data flow of content is allowed.
  \item \textbf{Decentralisation} \\
  Wherever possible a decentralised service should be favoured over a centralised one.
  \item \textbf{Real-world Use} \\
  Establish whether a system would be practical for use by real people under real circumstances with real data. A practical application is central to the project's success.
  \item \textbf{Permissions} \\
  A user should be able to administer permissions for data they own
  \item \textbf{Group access} \\
  A successful implementation will allow group access under the same permissions as are available to an individual
  \item \textbf{Accessibility} \\
  The project should use technologies that can be integrated and used by current software where applicable.
\end{itemize}
