\subsubsection{Group Permissions}

\paragraph{Extending Individual Access Control}

Group permissions extend the above system for individual permissions and require the use of smart contracts.

Whilst our application is intended to be fully decentralised, the key stakeholders for some applications (such as health care) may require access to the network to administrate. One example of this is the involvement of the GMC in validating doctor identities. If a doctor has not been registered, or has been struck off, they should not have any access to patient data (even if they claim to be a doctor). They should only have access should the GMC validate that they are in fact a valid doctor.

The idea of a group administrator, such as the GMC, conflicts with the idea of the data owner maintaining full access control and administration. However, should the data owner decide that the group should no longer have any access or wishes to change group permissions, they are able to do so.

To facilitate this, let's take a look at the architecture of a group's interactions with a particular identity's contract.

\input{tikz/architecture/group_interactions}

An identity claiming to be a member of a group will always interact with the storage contract it is trying to retrieve from or add data to. A group itself will never be able to directly affect or transact with a storage contract such that no malicious attacker would be able to pseudo-anonymously act as the group.

When the identity tries to access a path, their identity is cross-checked with the group they claim to be a member of. Should this group validate the identity as a member, and assuming the group has the necessary permissions that are required to action the identity's transaction, the transaction will be successful.

\paragraph{Group Key Sharing}

Whilst the process of writing data is similar to an individual (other than the membership validation above), the process of reading data differs hugely for groups.

If we were to extend the process of reading as an individual to a group, the result would be a process similar to that shown in figure \ref{fig:encryption_group_read_theoretical}.

\input{tikz/encryption/group_read}

Given the non-transitive nature of the proxy re-encryption scheme we are using, the process shown in figure \ref{fig:encryption_group_read_theoretical} doesn't allow end-to-end encryption. After the first stage of re-encryption, $\text{Data}_{G}$ represents a first-level encryption under the group $G$'s public key. Since the proxy re-encryption scheme being used only allows re-encryption from a second-level encryption to a first-level encryption (to eliminate transitivity), no further action is possible. Another process is required to facilitate group read.

If only one re-encryption is possible, the identity we re-encrypted for becomes the main priority. We ask ourselves whether the original (individual) scheme could work here, and indeed it could, although it comes with flaws described below.

\begin{itemize}
  \item 
  	\textbf{Non-optimal key storage} \\
    For every member of the group, a re-encryption key must be generated by the storage contract owner. The process of generating a re-encryption key for every member is $O(n)$, i.e. for a group with a membership of 50, 50 re-encryption keys need to be generated.
  \item
  	\textbf{Interaction: Member joins} \\
    When a member joins the group, the storage contract owner is required to generate a re-encryption key for the member such that the member can read data
  \item
  	\textbf{Interaction: Member leaves} \\
    When a member leaves the group, the storage contract owner must revoke the re-encryption key generated for the user. Since there may be a time difference between the group removing the member and the storage contract owner revoking the re-encryption key, this difference is exploitable by the member.
\end{itemize}

As an improvement to individual keys, let's take another look at the viability of the theoretical group read process.

Let's assume that there is a group key pair (specifically for encryption). When a member of the group requests data from a storage contract, they receive the data encrypted for the storage contract owner and a re-encryption key $re_{SCO \rightarrow G}$. They are able to use this pair to re-encrypt the data received to be $D_{G}$. 

\input{tikz/encryption/group_read_practical}

The following now apply:

\begin{itemize}
  \item The data is encrypted such that the group private key is required to decrypt it
  \item The group private key is encrypted using the group public key such that it can only be decrypted by itself
  \item The administrator $A$ of the group $G$ must have a re-encryption key $re_{G \rightarrow A}$ available such that they can create further re-encryption keys and manage the group.
\end{itemize}

When a member joins the group, the administrator creates a re-encryption key for them such that they are able to re-encrypt and then decrypt the group's private key. However, when a member leaves the group, the reference to their re-encryption key is removed from the group contract. It is likely that the group administrator would want to create a new key pair when a member leaves, to ensure no valuable data can be kept (encryption or re-encryption keys). Once the previous key pair has been invalidated a re-encryption key must be generated by the storage contract owner, requiring a level of interactivity between a group and a storage contract owner.

In contrast to figure \ref{fig:encryption_group_read_theoretical}, the process of receiving data as a member of the group now follows a process similar to that shown in figure \ref{fig:encryption_group_read_practical}.

Whilst the differences in the two schemes for group key sharing above are subtle, their differences become apparent when considered at scale.

\begin{table}[H]
  \centering
  
  \textbf{Giving Read Permission} \\
  \begin{tabular}{ | l | c | c | c | }
    \hline
    No. Storage Contract & Group Membership & Scheme 1 & Scheme 2 \\
    \hline
    1 & 50 & 50 & 51 \\
    10 & 50 & 500 & 60 \\
    100,000 & 100,000 & $10^{10}$ & 200,000 \\
    \hline
  \end{tabular}
  
  \vspace{5mm}
  
  \textbf{Revoking Read Permission} \\
  \begin{tabular}{ | l | c | c | c | }
    \hline
    No. Storage Contract & Group Membership & Scheme 1 & Scheme 2 \\
    \hline
    1 & 50 & 50 & 1 \\
    10 & 50 & 500 & 10 \\
    100,000 & 100,000 & $10^{10}$ & 100,000 \\
    \hline
  \end{tabular}
  
  \vspace{5mm}
  
  \textbf{Member Joins} \\
  \begin{tabular}{ | l | c | c | c | }
    \hline
    No. Storage Contract & Group Membership & Scheme 1 & Scheme 2 \\
    \hline
    1 & 50 & 1 & 1 \\
    10 & 50 & 10 & 1 \\
    100,000 & 100,000 & 100,000 & 1 \\
    \hline
  \end{tabular}
  
  \vspace{5mm}
  
  \textbf{Member Leaves} \\
  \begin{tabular}{ | l | c | c | c | }
    \hline
    No. Storage Contract & Group Membership & Scheme 1 & Scheme 2 \\
    \hline
    1 & 50 & 1 & 51 \\
    10 & 50 & 10 & 60 \\
    100,000 & 100,000 & 100,000 & 200,000 \\
    \hline
  \end{tabular}
  
  \caption{
    Comparison of group key sharing scheme complexity
  }{
    A comparison between schemes whereby the storage contract owner and the group administrator are required to distribute re-encryption keys. Comparison over the number of storage contracts an arbitrary group can read from, with membership as shown.
  }
  \label{table:group_key_sharing_scheme_comparison}
\end{table}

As shown above in table \ref{table:group_key_sharing_scheme_comparison}, the complexity of the two schemes differ hugely. We take $n$ as the number of storage contracts for which the group has read permissions, and $m$ as the group membership. 

The former scheme (scheme 1 above), modeled on individual permissions, has a complexity of $O(n \times m)$ for giving / revoking read permission - each storage contract owner must create / revoke a re-encryption key for every member of the group. When a member joins / leaves a group, each storage contract owner must create / revoke a re-encryption key, $O(n)$.

The latter scheme (scheme 2 above), segregating group and member key management, has a complexity of $O(n + m)$ for giving read permission or a member leaving - each storage contract owner must create a (new) re-encryption key for the group, with the group administrator responsible for re-encryption keys for the members. When a storage contract owner revokes the group's read permission they only need to revoke the group's re-encryption key $O(1)$ per storage contract owner. When a member leaves, regardless of the number of storage contracts it affects, revoking their access is $O(1)$.

In context of the health care use case of this project, the difference between the above complexities decides the success of a project. Since the latter scheme has a lower upper bound for complexity of $O(n + m)$ over its set of operations, in a health care scenario, it would be advisable that groups are sufficiently large to cover the most likely of circumstances, but not too large that a change in membership incurs a heavy computational cost.
